Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

\section{Fitting models to the \mFps}\label{sec:app:ind}
In order to perform the fit, the noise in the \mFps\ must be
estimated.  To do that, the power distributions of Section
\ref{sec:anal} are considered.  The Fourier power at a given pixel is
not independent of the Fourier power at another pixel.  This is
because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.

@@

\subsection{Model fitting and selection}
The \mFpa\ are assumed to be normally distributed with a width given
by $\sigma_{mean}$ as calculated above.  Equations \ref{eqn:pwrlaw}
and \ref{eqn:pwrlawbump} are fit to the geometric mean power spectra
shown in Figures \ref{fig:fit171193}.  A five step fitting process is
used to fit Models 1 and 2 to the data. The maximum likelihood
function is constructed using PyMC version 2.3
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}. Maximum likelihood
estimates are found using SciPy version 0.13.2 \citep{scipy,
  scientificpython} via Powell's minimization method
\citep{Powell01011964, wpress86:numerical}.

\begin{enumerate}
\item Maximum likelihood estimates to the values of the parameters of
  Model 1 are found using the distribution widths $\sigma$.  Since
  these widths are much larger than $\sigma_{mean}$ is much wider than
  the standard error in the mean, it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The estimated values to the Model 1 parameters are then used as
  initial guesses to the second estimate of the Model 1
  parameters. Maximum likelihood estimates to the values of the
  parameters of Model 1 are found using the distribution widths
  $\sigma_{mean}$, seeded with estimated parameter values from step 1.
  This generates a better estimate to the parameters of the model
  fit.  The resulting parameter estimates are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma$, seeded with the maximum likelihood parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item Model 2 is fit to the data using the maximum likelihood Model 2
  parameter values at Step 4 and the widths $\sigma_{mean}$.  The
  resulting parameter estimates are the final estimates for Model 2.
\end{enumerate}

>>>>

\section{Fitting models to the \mFps}\label{sec:app:ind}
In order to perform the fit, the noise in the \mFps\ (black lines,
Figure \ref{}) must be estimated.  To do that, the power distributions
of Section \ref{sec:anal} are considered.  The Fourier power at a
given pixel is not independent of the Fourier power at another pixel.
This is because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.

@@

\subsection{Model fitting and selection}
The \mFpa\ are assumed to be normally distributed with a width given
by $\sigma_{mean}$ as calculated above.  Equations \ref{eqn:pwrlaw}
and \ref{eqn:pwrlawbump} are fit to the geometric mean power spectra
shown in Figures \ref{fig:fit171193}.  A five step fitting process is
used to fit Models 1 and 2 to the data.  A Bayesian/Markov chain Monte
Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  The likelihood

Each of the priors for the parameters in each model has a uniform
distribution, and are given in Table \ref{tab:priors}.  Each MCMC
chain takes 100,000 samples, with burn-in assumed to be at 50,000
samples.  The chain is thinned by taking every fifth element in the
chain, forming the final sample from which the parameter estimates and
their uncertainties are calculated.

\begin{deluxetable}{cccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Region} &
\colhead{$N_{pixel}$} &
\colhead{Waveband} &
\colhead{$N_{eff}$} \\
}
\startdata
loop footpoints & 2000 & 171\AA & 183 \\
                &     & 193\AA & 185 \\
moss            & 2100 & 171\AA & 629 \\
                &     & 193\AA & 521 \\
quiet Sun       & 2500 & 171\AA & 598 \\
                &     & 193\AA & 639 \\
sunspot         & 7500 & 171\AA & 1505 \\
                &     & 193\AA & 1531 \\
\enddata
\end{deluxetable}

The maximum likelihood
function is constructed using. Maximum likelihood
estimates are found using SciPy version 0.13.2 \citep{scipy,
  scientificpython} via Powell's minimization method
\citep{Powell01011964, wpress86:numerical}.

\begin{enumerate}
\item

Maximum likelihood estimates to the values of the parameters of
  Model 1 are found using the distribution widths $\sigma$.  Since
  these widths are much larger than $\sigma_{mean}$ is much wider than
  the standard error in the mean, it allows the fitting algorithm to
  converge to an approximate fit solution.
\item The estimated values to the Model 1 parameters are then used as
  initial guesses to the second estimate of the Model 1
  parameters. Maximum likelihood estimates to the values of the
  parameters of Model 1 are found using the distribution widths
  $\sigma_{mean}$, seeded with estimated parameter values from step 1.
  This generates a better estimate to the parameters of the model
  fit.  The resulting parameter estimates are the final estimates for
  Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma$, seeded with the maximum likelihood parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item Model 2 is fit to the data using the maximum likelihood Model 2
  parameter values at Step 4 and the widths $\sigma_{mean}$.  The
  resulting parameter estimates are the final estimates for Model 2.
\end{enumerate}

The 68\% credible intervals for the parameters are quoted in Table
\ref{tab:parameters}.  The upper and lower limits to the credible
intervals are found by determining the values beyond which 16\% of the
probability lies in each wing of the marginal distributions.
